---
title: "Final Assignment - Code"
output: html_document
date: "2024-04-28"
---

Reading the original file and selecting the songs that are:
- between years 1940 and 2019
- removing "misc" genre
- Selecting only songs in English
- Selecting only songs that have more than 50 views

Saving the result of this filter as "sub_songs"

After that, selecting the top 250 songs of each year and saving the resulting dataset as "top_songs_per_year"

```{r}
# #all_songs <- read_csv(unz("archive_2.zip", "song_lyrics.csv"))
# all_songs <- read_csv("song_lyrics.csv")
# sub_songs <- all_songs[all_songs$year >= 1940 & all_songs$year <= 2019 & all_songs$tag != "misc" & all_songs$views > 50 & all_songs$language == "en",]
#
# Visualizing the data format
# table(sub_songs$language)
# table(sub_songs$year)
# table(sub_songs$tag)
# str(sub_songs)
#
# Subsetting the 250 top songs per year
# top_songs_per_year <- sub_songs %>%
#   arrange(year, desc(views)) %>%
#   group_by(year) %>%
#   slice_head(n = 250) %>%
#   ungroup()
#
# #since not all years have 250 songs, we need to remove the rows that are empty
# top_songs_per_year <- top_songs_per_year[complete.cases(top_songs_per_year),]
#
# # View the first few rows of the new dataset
# head(top_songs_per_year)
# table(top_songs_per_year$tag, top_songs_per_year$year)
#
# saveRDS(sub_songs, "sub_songs.rds")
# saveRDS(top_songs_per_year, "top_songs_per_year.rds")

# Loading the data from the RDS files
#sub_songs <- readRDS("sub_songs.rds")
top_songs_per_year <- readRDS("top_songs_per_year.rds")
```

Analysing the data, to see the distribution of genres throughout the years to create the Plot 1 of the final assignment

```{r}
# Summarizing the data
tag_counts_per_year <- top_songs_per_year %>%
  group_by(year, tag) %>%
  summarise(count = n(), .groups = 'drop')

tag_counts_per_year <- tag_counts_per_year %>%
  mutate(clean_tag = case_when(
    tag == "country" ~ "Country",
    tag == "pop" ~ "Pop",
    tag == "rap" ~ "Rap",
    tag == "rb" ~ "R&B",
    tag == "rock" ~ "Rock",
    TRUE ~ as.character(tag)  # Keeps the tag unchanged if it doesn't match any of the specified values
  ))

# Define a new, softer color palette
color_palette <- brewer.pal(min(n_distinct(tag_counts_per_year$clean_tag), 8), "Set1")

plot1 <- ggplot(tag_counts_per_year, aes(x = year, y = count, group = clean_tag, color = clean_tag)) +
  geom_line(size = 1) + # Keep lines slightly thicker for visibility
  scale_color_manual(values = color_palette) + # Apply the new color palette
  theme_minimal(base_size = 14) + # Continue with a minimal theme and readable base font size
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 12),
    plot.title = element_text(face = "bold", hjust = 0, size = 16),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title = element_text(size = 14)
  ) +
  labs(
    title = "Plot 1: Genres of Most Popular Songs of the Year",
    x = "Year",
    y = "Number of Songs"
  ) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) # Adjust x-axis breaks for readability

ggsave("plot1.png", plot1, width = 10, height = 5, dpi = 300)

```
Starting pre processing of the dataset

```{r, eval = FALSE}
# Checking the format of the lyrics for pre processing
head(top_songs_per_year$lyrics)
```

Identifying the number of lines and cleaning the lyrics of the dataset

```{r}
#removing the information in square brackets
lyrics_clean <- gsub("\\[.*?\\]", "", top_songs_per_year$lyrics)

#Getting the number of lines of the song
all_n_lines <- sapply(lyrics_clean, function(x){
  #Splitting the song into lines
  split_song <- strsplit(x, "\n")[[1]]
  #Getting the number of lines in the song
  lines <- length(split_song)[split_song != ""]
  n_lines <- length(lines)
  return(n_lines)
  })

#replacing the new line characters with a space
lyrics_clean <- gsub("\n", " ", lyrics_clean)

#including the new info in the dataset
top_songs_per_year$n_lines <- all_n_lines
top_songs_per_year$clean_lyrics <- lyrics_clean
```


```{r}
#Pre processing and creating corpus and dfm
corpus <- corpus(top_songs_per_year,
                 text_field = "clean_lyrics")

toks <- tokens(corpus, remove_punct = TRUE, remove_url=TRUE, remove_numbers = TRUE, remove_symbols = TRUE,  verbose=TRUE)

toks <- tokens_remove(toks, pattern = c(stopwords("en"), "t.co", "https", "rt", "amp", "http", "t.c", "can", "u", "t", "htt", "s", "w", "y"))

dfm <- dfm(toks, verbose=TRUE, tolower = TRUE)
docnames(dfm) <- paste(top_songs_per_year$title, top_songs_per_year$year, sep = " - ")
docvars(dfm)
```


```{r}
# Selecting the most repetitive songs from the dataset
# The Trashmen, “Surfin’ Bird” (1963)
surfin_bird <- which(top_songs_per_year$artist == "The Trashmen")
print(top_songs_per_year[which(top_songs_per_year$artist == "The Trashmen"),])

# Foo Fighters, “Best of You” (2005)
best_of_you <- which(top_songs_per_year$title == "Best of You")
print(top_songs_per_year[which(top_songs_per_year$title == "Best of You"),])

# Red Hot Chili Peppers, “Give It Away” (1991)
give_it_away <- which(top_songs_per_year$artist == "Red Hot Chili Peppers" & top_songs_per_year$title == "Give It Away")
print(top_songs_per_year[which(top_songs_per_year$artist == "Red Hot Chili Peppers" & top_songs_per_year$title == "Give It Away"),])
```

```{r}
# Selecting complex songs
bohe <- which(top_songs_per_year$title == "Bohemian Rhapsody")
stair <- which(top_songs_per_year$title == "Stairway to Heaven" & top_songs_per_year$artist == "Led Zeppelin")
hurrycane <- which(top_songs_per_year$title == "Hurricane")

#subsetting the repetitive and complex songs
complex_subset <- c(bohe, stair, hurrycane)
rep_subset <- c(surfin_bird, best_of_you, give_it_away)

method_eval <- top_songs_per_year[c(complex_subset, rep_subset),]
```


```{r}
library(brotli)

#Measuring compression
method_eval$compression_rate <- sapply(method_eval$clean_lyrics, function(x){
  #Transforming to raw
  to_raw <- charToRaw(x)
  original_length <- length(to_raw)
  compressed <- brotli_compress(to_raw, quality = 11, window = 22)
  compressed_length <- length(compressed)
  return(1 -(compressed_length/original_length))
})
```


```{r}
#Subseting the dfm
selected_dfm <- dfm[c(rep_subset, complex_subset),]

# Counting the total unique words per song
# same as the number of columns that have value greater than zero
tot_unique_words <- rowSums(selected_dfm > 0)

# Average word repetition in a song
# Initialize an empty vector to store the average word repetition for each selected song
avg_word_repetition <- numeric(nrow(selected_dfm))

# For every row of the dfm
for (i in 1:nrow(selected_dfm)) {
  # Select the row
  row <- selected_dfm[i, ]
  
  # Remove columns that are equal to zero
  non_zero_values <- row[row > 0]
  
  # Calculate the average of the row
  avg_word_repetition[i] <- mean(non_zero_values)
}

#Lexical Diversity - Total Unique words/total words
lexical_diversity <- tot_unique_words/rowSums(selected_dfm)

#Readability
subset <- top_songs_per_year$lyrics[c(rep_subset, complex_subset)]
readability <- textstat_readability(subset, "meanWordSyllables")[,2]

#average unique words per line
subset_n_lines <- top_songs_per_year$n_lines[c(rep_subset, complex_subset)]
avg_unique_words_per_line <- tot_unique_words/subset_n_lines

#Including new variables in the dataset
method_eval$unique_words <- tot_unique_words
method_eval$avg_word_repetition <- avg_word_repetition
method_eval$lexical_diversity <- lexical_diversity
method_eval$readability <- readability
method_eval$avg_unique_words_per_line <- as.numeric(avg_unique_words_per_line)

```


```{r}
songs_data_long <- pivot_longer(plot_data, cols=c(unique_words, avg_word_repetition, lexical_diversity, readability, avg_unique_words_per_line), names_to="Measure", values_to="Value")

value_map <- c(compression_rate = "Compression Rate",
               unique_words = "Total Unique Words",
               avg_word_repetition = "Avg Word Repetition",
               lexical_diversity = "Lexical Diversity",
               readability = "Readability",
               avg_unique_words_per_line = "Avg Unique Words per Line")

songs_data_long <- songs_data_long %>%
  mutate(Measure = recode(Measure, !!!value_map))

# Create violin plots for all measures, faceted by Measure
p <- ggplot(songs_data_long, aes(x=category, y=Value, fill=category)) +
  geom_violin(trim=TRUE) +  # trim=FALSE shows the full distribution
  facet_wrap(~Measure, scales="free_y", ncol=2) +  # Adjust the number of columns if needed
  labs(title="Plot 2: Song Measures by Category",
       x="",
       y="Value",
       fill="") +
  theme_minimal(base_size = 14) +  # Increase base font size
  scale_fill_manual(values=c("Repetitive"="blue", "Complex"="orange")) +
  theme(legend.position="",  # Move legend to the bottom
        strip.text.x = element_text(size = 11, face = "bold"),  # Customize facet labels
        axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x axis texts for better readability
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),)  # Center plot title

# Print the plot
print(p)

# Save the plot with adjusted dimensions and higher resolution
ggsave("plot3_violin.png", plot = p, width = 6, height = 6, dpi = 300)


```


```{r}
#Measuring unique words per song
tot_unique_words <- rowSums(dfm > 0)

#Average word repetition in a song
# Initialize an empty vector to store the average word repetition for each selected song
avg_word_repetition <- numeric(nrow(dfm))

# For every row of the dfm
for (i in 1:nrow(dfm)) {
  # Select the row
  row <- dfm[i, ]
  
  # Remove columns that are equal to zero
  non_zero_values <- row[row > 0]
  
  # Calculate the average of the row (assuming you want to exclude any non-numeric first column, which should not be present in a typical DFM)
  # Since DFMs are numeric matrices, you can directly calculate the average of non-zero values
  avg_word_repetition[i] <- mean(non_zero_values)
}

#Lexical Diversity - Unique words/total words
lexical_diversity <- tot_unique_words/rowSums(dfm)

#average unique words per line
avg_unique_words_per_line <- tot_unique_words/top_songs_per_year$n_lines

#Readability
library(quanteda.textstats)
# subset <- top_songs_per_year$lyrics
# b <- gsub("\n", " ", subset)
# b <- gsub("\\[.*?\\]", "", b)

readability <- textstat_readability(top_songs_per_year$clean_lyrics, "meanWordSyllables")[,2]

#Including new variables in the dataset
top_songs_per_year$unique_words <- tot_unique_words
top_songs_per_year$avg_word_repetition <- avg_word_repetition
top_songs_per_year$lexical_diversity <- lexical_diversity
top_songs_per_year$readability <- readability
top_songs_per_year$avg_unique_words_per_line <- avg_unique_words_per_line
top_songs_per_year$decade <- paste(substr(top_songs_per_year$year, 1, 3), "0s", sep = "")

top_songs_per_year <- top_songs_per_year %>%
  mutate(clean_tag = case_when(
    tag == "country" ~ "Country",
    tag == "pop" ~ "Pop",
    tag == "rap" ~ "Rap",
    tag == "rb" ~ "R&B",
    tag == "rock" ~ "Rock",
    TRUE ~ as.character(tag)  # Keeps the tag unchanged if it doesn't match any of the specified values
  ))


```
Making the plots


```{r}
library(ggplot2)
library(patchwork)

plot_list <- list()
measures <- c("unique_words", "avg_word_repetition", "lexical_diversity", "readability", "avg_unique_words_per_line")
clean_measures <- c("Unique Words", "Average Word Repetition", "Lexical Diversity", "Readability", "Average Unique Words per Line")

for (measure in measures) {
  i <- which(measures == measure)
  p <- ggplot(top_songs_per_year, aes(x = year, y = .data[[measure]], color = clean_tag)) +
    geom_point(size = .5, alpha = .8) +
    theme_minimal() +
    labs(title = paste(i, ". ", clean_measures[i], "Over Time"), x = "", y = "")+
    theme(legend.title = element_blank(), legend.position = "bottom",
          title = element_text(size = 8, hjust = 0.5),
          axis.text.y = element_text(size = 6))
  
  # Remove the legend except for the first plot
  if (measure != measures[5]) {
    p <- p + theme(legend.position = "none")
  }
  
  plot_list[[measure]] <- p
}

# Combine all plots, keeping the legend only in the first plot
plot_grid <- wrap_plots(plot_list, ncol = 2)

# Print the combined plot
#plot_grid

# Add a common title with plot_annotation() and adjust the layout with plot_layout()
plot_grid <- plot_grid + 
  plot_annotation(
    title = "Plot 3: Evolution of Musical Attributes Over Time",
    theme = theme(
      plot.title = element_text(hjust = 0, face = "bold")
    )
  )

  # Display the combined plot with the common title
print(plot_grid)

# Save the plot as a PNG file
ggsave("./plots/plot3_combined_plot.png", plot_grid, width = 16, height = 14 , units = "cm", dpi = 450)

```


```{r}
#Unique words plot
p_uni <- ggplot(top_songs_per_year, aes(x = decade, y = unique_words)) +
  geom_boxplot(outlier.colour = "gray45", colour = "gray35", outlier.size = .7) +
  #scale_y_log10() +  # Transform the y-axis to a log scale
  scale_y_continuous(limits = c(0,400))+
  theme_minimal() +
theme(title = element_text(size = 8, hjust = 0.5),
          axis.text.y = element_text(size = 6,),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  #scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  #facet_wrap(~clean_tag, scales = "free_y") +
  labs(title = paste("1. Total Unique Words Distribution Over Time"), x = "", y = "")
print(p_uni)

p_rep <- ggplot(top_songs_per_year, aes(x = decade, y = avg_word_repetition)) +
  geom_boxplot(outlier.colour = "gray85", colour = "gray35", outlier.size = .7) +
  #scale_y_log10() +  # Transform the y-axis to a log scale
  scale_y_continuous(limits = c(0,5))+
  theme_minimal() +
  theme(title = element_text(size = 8, hjust = 0.5),
          axis.text.y = element_text(size = 6),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  #scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  #facet_wrap(~clean_tag, scales = "free_y") +
  labs(title = paste("2. Average Word Repetition"), x = "", y = "")
print(p_rep)

p_lex <- ggplot(top_songs_per_year, aes(x = decade, y = lexical_diversity)) +
  geom_boxplot(outlier.colour = "gray85", colour = "gray35", outlier.size = .7) +
  #scale_y_log10() +  # Transform the y-axis to a log scale
  scale_y_continuous(limits = c(0,1.2))+
  theme_minimal() +
  theme(title = element_text(size = 8, hjust = 0.5),
          axis.text.y = element_text(size = 6),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  #scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  #facet_wrap(~clean_tag, scales = "free_y") +
  labs(title = paste("3. Lexical DiversityOver Time"), x = "", y = "")
p_lex

p_read <- ggplot(top_songs_per_year, aes(x = decade, y = readability)) +
  geom_boxplot(outlier.colour = "gray85", colour = "gray35", outlier.size = .7) +
  #scale_y_log10() +  # Transform the y-axis to a log scale
  scale_y_continuous(limits = c(1.1,1.3))+
  theme_minimal() +
theme(title = element_text(size = 8, hjust = 0.5),
          axis.text.y = element_text(size = 6),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  #scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  #facet_wrap(~clean_tag, scales = "free_y") +
  labs(title = paste("4. Mean Word Syllables Over Time"), x = "", y = "")
p_read

p_avg <- ggplot(top_songs_per_year, aes(x = decade, y = avg_unique_words_per_line)) +
  geom_boxplot(outlier.colour = "gray85", colour = "gray35", outlier.size = .7) +
  #scale_y_log10() +  # Transform the y-axis to a log scale
  scale_y_continuous(limits = c(0,5))+
  theme_minimal() +
theme(title = element_text(size = 8, hjust = 0.5),
          axis.text.y = element_text(size = 6),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  #scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  #facet_wrap(~clean_tag, scales = "free_y") +
  labs(title = paste("5. Unique Words per Line Over Time"), x = "", y = "")
p_avg

plot_grid <- p_uni + p_rep + p_lex + p_read + p_avg +
  plot_annotation(
    title = "Plot 4: Distribution of Musical Attributes Over Time",
    theme = theme(
      plot.title = element_text(hjust = 0, face = "bold")
    )
  ) + plot_layout(ncol = 2)

  # Display the combined plot with the common title
print(plot_grid)

# Save the plot as a PNG file
ggsave("./plots/4_combined_plot_box_plot.png", plot_grid, width = 16, height = 17 , units = "cm", dpi = 450)

```

Making genre wordcloud


```{r warning=FALSE}
library(quanteda.textplots)
docvars(dfm)$clean_tag <- top_songs_per_year$clean_tag
dfm_grouped <- dfm_group(dfm, groups = docvars(dfm)$clean_tag)
textplot_wordcloud(dfm_grouped, comparison = TRUE)
```

```{r warning=FALSE}

par(mar = c(2, 1, 2, 1))
for (i in unique(docvars(dfm)$clean_tag)) {
    # Generate a word cloud for each unique tag
    textplot_wordcloud(
      dfm_subset(dfm, docvars(dfm)$clean_tag == i), 
      min_count = 10,
      max_words = 100,
      color = brewer.pal(8, "Dark2"),
      scale = c(8, 2)
    )
    # Add title using base R function
print(paste("Wordcloud for", i))
}
```

```{r}
color_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

# Adjusted plot to improve visibility of the regression line
p_uni <- ggplot(top_songs_per_year, aes(x = year, y = unique_words, color = clean_tag)) +
  geom_point(alpha = 0.1, size = 2) +
  #geom_jitter(alpha = 0.1, size = 2) +  # Use jitter to differentiate overlapping points
  geom_smooth(method = "lm", se = FALSE, color = "red", size = .5, aes(group = 1)) +  # Regression line across all data
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +
  scale_color_manual(values = color_palette) +  # Apply custom colors
  theme_minimal() +
  labs(title = "Plot 6.1: Unique Words Over Time", x = "Year", y = "") +
  scale_y_continuous(limits = c(0, 250)) +  # Adjusted limits to fit data
  scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +  # Adjusted x-axis breaks
  theme(axis.text.x = element_text(angle = 45, size = 7, hjust = 1),
        legend.position = "none",
        plot.title = element_text(size = 14, face = "bold", hjust = 0))# Adjusted x-axis breaks

print(p_uni)
ggsave("./plots/61_unique_words_genre_point.png", p_uni, width = 20, height = 7, units = "cm", dpi = 450)
```

```{r}
library(ggplot2)

p_uni_box <- ggplot(top_songs_per_year, aes(x = decade, y = unique_words, fill = clean_tag)) +
  geom_boxplot(alpha = 0.7, outlier.size = .7) +  # Add transparency to the boxplots
  scale_y_continuous(limits = c(0, 250)) +  # Adjust y-axis limits
  scale_fill_manual(values = color_palette) +  # Use a custom color palette
  theme_minimal(base_size = 14) +  # Use a minimal theme with a larger base font size
  theme(
    axis.title = element_text(size = 14),  # Make axis titles larger
    axis.text = element_text(size = 12),  # Increase axis text size
    plot.title = element_text(size = 16, face = "bold", hjust = 0),  # Increase plot title size and make it bold
    legend.position = "",  # Move legend to the bottom
    strip.background = element_blank(),  # Remove background from facet labels
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 7, angle = 45, hjust = 1) # Bold facet labels
  ) +
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +  # Organize facets in a 3-column layout
  labs(
    title = "Plot 6.2: Unique Words per Decade",
    x = "Decade",
    y = ""
  ) #+
 # guides(fill = guide_legend(title = "Genre"))  # Add a title to the legend

print(p_uni_box)
ggsave("./plots/62_unique_words_box.png", p_uni_box, width = 20, height = 7, units = "cm", dpi = 450)
```



```{r}
color_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

# Adjusted plot to improve visibility of the regression line
p_rep <- ggplot(top_songs_per_year, aes(x = year, y = avg_word_repetition, color = clean_tag)) +
  geom_point(alpha = 0.1, size = 2) +
  #geom_jitter(alpha = 0.1, size = 2) +  # Use jitter to differentiate overlapping points
  geom_smooth(method = "lm", se = FALSE, color = "red", size = .5, aes(group = 1)) +  # Regression line across all data
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +
  scale_color_manual(values = color_palette) +  # Apply custom colors
  theme_minimal() +
  labs(title = "Plot 7.1: Average Word Repetition Over Time", x = "Year", y = "") +
  scale_y_continuous(limits = c(0, 4)) +  # Adjusted limits to fit data
  scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +  # Adjusted x-axis breaks
  theme(axis.text.x = element_text(angle = 45, size = 7, hjust = 1),
        legend.position = "none",
        plot.title = element_text(size = 14, face = "bold", hjust = 0))# Adjusted x-axis breaks

print(p_rep)
ggsave("./plots/71_word_rep_point.png", p_rep, width = 20, height = 7, units = "cm", dpi = 450)
```


```{r}
library(ggplot2)

# Define a nicer color palette, assuming we have five levels in clean_tag
color_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

p_rep_box <- ggplot(top_songs_per_year, aes(x = decade, y = avg_word_repetition, fill = clean_tag)) +
  geom_boxplot(alpha = 0.7, outlier.size = .7) +  # Add transparency to the boxplots
  scale_y_continuous(limits = c(0.5 ,4)) +  # Adjust y-axis limits
  scale_fill_manual(values = color_palette) +  # Use a custom color palette
  theme_minimal(base_size = 14) +  # Use a minimal theme with a larger base font size
  theme(
    axis.title = element_text(size = 14),  # Make axis titles larger
    axis.text = element_text(size = 12),  # Increase axis text size
    plot.title = element_text(size = 16, face = "bold", hjust = 0),  # Increase plot title size and make it bold
    legend.position = "",  # Move legend to the bottom
    strip.background = element_blank(),  # Remove background from facet labels
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 7, angle = 45, hjust = 1) # Bold facet labels
  ) +
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +  # Organize facets in a 3-column layout
  labs(
    title = "Plot 7.2: Average Word Repetition Over Time Per Genre",
    x = "Decade",
    y = ""
  ) #+
 # guides(fill = guide_legend(title = "Genre"))  # Add a title to the legend

print(p_rep_box)
ggsave("./plots/72_word_rep_box.png", p_rep_box, width = 20, height = 7, units = "cm", dpi = 450)
```

```{r}
color_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

# Adjusted plot to improve visibility of the regression line
p_lex <- ggplot(top_songs_per_year, aes(x = year, y = lexical_diversity, color = clean_tag)) +
  geom_point(alpha = 0.1, size = 2) +
  #geom_jitter(alpha = 0.1, size = 2) +  # Use jitter to differentiate overlapping points
  geom_smooth(method = "lm", se = FALSE, color = "red", size = .5, aes(group = 1)) +  # Regression line across all data
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +
  scale_color_manual(values = color_palette) +  # Apply custom colors
  theme_minimal() +
  labs(title = "Plot 8.1: Lexical Diversity Over Time", x = "Year", y = "") +
  scale_y_continuous(limits = c(NA, NA)) +  # Adjusted limits to fit data
  scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +  # Adjusted x-axis breaks
  theme(axis.text.x = element_text(angle = 45, size = 7, hjust = 1),
        legend.position = "none",
        plot.title = element_text(size = 14, face = "bold", hjust = 0))# Adjusted x-axis breaks

print(p_lex)
ggsave("./plots/81_lex_point.png", p_lex, width = 20, height = 7, units = "cm", dpi = 450)
```


```{r}
library(ggplot2)

# Define a nicer color palette, assuming we have five levels in clean_tag
color_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

p_lex_box <- ggplot(top_songs_per_year, aes(x = decade, y = lexical_diversity, fill = clean_tag)) +
  geom_boxplot(alpha = 0.7, outlier.size = .7) +  # Add transparency to the boxplots
  #scale_y_continuous(limits = c(0.5 ,4)) +  # Adjust y-axis limits
  scale_fill_manual(values = color_palette) +  # Use a custom color palette
  theme_minimal(base_size = 14) +  # Use a minimal theme with a larger base font size
  theme(
    axis.title = element_text(size = 14),  # Make axis titles larger
    axis.text = element_text(size = 12),  # Increase axis text size
    plot.title = element_text(size = 16, face = "bold", hjust = 0),  # Increase plot title size and make it bold
    legend.position = "",  # Move legend to the bottom
    strip.background = element_blank(),  # Remove background from facet labels
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 7, angle = 45, hjust = 1) # Bold facet labels
  ) +
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +  # Organize facets in a 3-column layout
  labs(
    title = "Plot 8.2: Lexical Diversity Over Per Decade",
    x = "Decade",
    y = ""
  ) #+
 # guides(fill = guide_legend(title = "Genre"))  # Add a title to the legend

print(p_lex_box)
ggsave("./plots/82_lex_box.png", p_lex_box, width = 20, height = 7, units = "cm", dpi = 450)

```

```{r}
color_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

# Adjusted plot to improve visibility of the regression line
p_read <- ggplot(top_songs_per_year, aes(x = year, y = readability, color = clean_tag)) +
  geom_point(alpha = 0.1, size = 2) +
  #geom_jitter(alpha = 0.1, size = 2) +  # Use jitter to differentiate overlapping points
  geom_smooth(method = "lm", se = FALSE, color = "red", size = .5, aes(group = 1)) +  # Regression line across all data
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +
  scale_color_manual(values = color_palette) +  # Apply custom colors
  theme_minimal() +
  labs(title = "Plot 9.1: Mean Word Syllables Over Time", x = "Year", y = "") +
  scale_y_continuous(limits = c(1, 1.4)) +  # Adjusted limits to fit data
  scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +  # Adjusted x-axis breaks
  theme(axis.text.x = element_text(angle = 45, size = 7, hjust = 1),
        legend.position = "none",
        plot.title = element_text(size = 14, face = "bold", hjust = 0))# Adjusted x-axis breaks

print(p_read)
ggsave("./plots/91_read_point.png", p_read, width = 20, height = 7, units = "cm", dpi = 450)
```


```{r}
library(ggplot2)

# Define a nicer color palette, assuming we have five levels in clean_tag
color_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

p_read_box <- ggplot(top_songs_per_year, aes(x = decade, y = readability, fill = clean_tag)) +
  geom_boxplot(alpha = 0.7, outlier.size = .7) +  # Add transparency to the boxplots
  scale_y_continuous(limits = c(1.1 ,1.3)) +  # Adjust y-axis limits
  scale_fill_manual(values = color_palette) +  # Use a custom color palette
  theme_minimal(base_size = 14) +  # Use a minimal theme with a larger base font size
  theme(
    axis.title = element_text(size = 14),  # Make axis titles larger
    axis.text = element_text(size = 12),  # Increase axis text size
    plot.title = element_text(size = 16, face = "bold", hjust = 0),  # Increase plot title size and make it bold
    legend.position = "",  # Move legend to the bottom
    strip.background = element_blank(),  # Remove background from facet labels
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 7, angle = 45, hjust = 1) # Bold facet labels
  ) +
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +  # Organize facets in a 3-column layout
  labs(
    title = "Plot 9.2: Mean Word Syllables Over Time Per Genre",
    x = "Decade",
    y = ""
  ) #+
 # guides(fill = guide_legend(title = "Genre"))  # Add a title to the legend

print(p_read_box)
ggsave("./plots/92_read_box.png", p_read_box, width = 20, height = 7, units = "cm", dpi = 450)
```

```{r}
color_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

# Adjusted plot to improve visibility of the regression line
p_avg <- ggplot(top_songs_per_year, aes(x = year, y = avg_unique_words_per_line, color = clean_tag)) +
  geom_point(alpha = 0.1, size = 2) +
  #geom_jitter(alpha = 0.1, size = 2) +  # Use jitter to differentiate overlapping points
  geom_smooth(method = "lm", se = FALSE, color = "red", size = .5, aes(group = 1)) +  # Regression line across all data
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +
  scale_color_manual(values = color_palette) +  # Apply custom colors
  theme_minimal() +
  labs(title = "Plot 10.1: Average Unique Words per Line Over Time", x = "Year", y = "") +
  scale_y_continuous(limits = c(0.5, 4)) +  # Adjusted limits to fit data
  scale_x_discrete(breaks = c(1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +  # Adjusted x-axis breaks
  theme(axis.text.x = element_text(angle = 45, size = 7, hjust = 1),
        legend.position = "none",
        plot.title = element_text(size = 14, face = "bold", hjust = 0))# Adjusted x-axis breaks

print(p_avg)
ggsave("./plots/101_avg_uni_point.png", p_avg, width = 20, height = 7, units = "cm", dpi = 450)
```


```{r}
library(ggplot2)

# Define a nicer color palette, assuming we have five levels in clean_tag
color_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")

p_avg_box <- ggplot(top_songs_per_year, aes(x = decade, y = avg_unique_words_per_line, fill = clean_tag)) +
  geom_boxplot(alpha = 0.7, outlier.size = .7) +  # Add transparency to the boxplots
  scale_y_continuous(limits = c(0.5,4)) +  # Adjust y-axis limits
  scale_fill_manual(values = color_palette) +  # Use a custom color palette
  theme_minimal(base_size = 14) +  # Use a minimal theme with a larger base font size
  theme(
    axis.title = element_text(size = 14),  # Make axis titles larger
    axis.text = element_text(size = 12),  # Increase axis text size
    plot.title = element_text(size = 16, face = "bold", hjust = 0),  # Increase plot title size and make it bold
    legend.position = "",  # Move legend to the bottom
    strip.background = element_blank(),  # Remove background from facet labels
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 7, angle = 45, hjust = 1) # Bold facet labels
  ) +
  facet_wrap(~clean_tag, scales = "free_y", nrow = 1) +  # Organize facets in a 3-column layout
  labs(
    title = "Plot 10.2: Average Unique Words per Line Over Time",
    x = "Decade",
    y = ""
  ) #+
 # guides(fill = guide_legend(title = "Genre"))  # Add a title to the legend

print(p_avg_box)
ggsave("./plots/102_avg_uni_box.png", p_avg_box, width = 20, height = 7, units = "cm", dpi = 450)
```
